---
title: "Predictions: full results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Predictions: full results}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina = 3, # change to 3 
  fig.align = "center",
  warning = FALSE,
  fig.width = 7,
  fig.height = 4,
  #dev.args = list(bg = "transparent"),
 # fig.ext = "svg",
  echo = FALSE
)
```

```{r setup}
library(CauseSpecCovarMI)
library(ggplot2)
library(ggpubr)

theme_set(
  theme_minimal(base_size = 12)
)

set.seed(1984)
```


```{r read}
# Read-in summarised results and scenarios
preds_results <- data.table::setDT(CauseSpecCovarMI::preds_results)

preds_results <- preds_results[
  n != 500 & state != "EFS" &  
    m %in% c(0, 50) & 
    `combo-X_Z` %in% c(
      "mean_X-Z_mean", 
      "-1SD_X-Z_-1SD", 
      "+1SD_X-Z_+1SD",
      "0_X-Z_mean", 
      "0_X-Z_-1SD", 
      "1_X-Z_+1SD"
    )
]

# Get factor order right
preds_results[, `combo-X_Z` := factor(
  `combo-X_Z`,
  levels = c(
    "mean_X-Z_mean",
    "0_X-Z_mean", 
    "-1SD_X-Z_-1SD",
    "0_X-Z_-1SD", 
    "+1SD_X-Z_+1SD",
    "1_X-Z_+1SD"
  )
)]

patient_labs <- ggplot2::as_labeller(c(
  "+1SD_X-Z_+1SD" = "High risk", 
  "-1SD_X-Z_-1SD" = "Low risk",
  "mean_X-Z_mean" = "Baseline",
  "1_X-Z_+1SD" = "High risk",
  "0_X-Z_-1SD" = "Low risk",
  "0_X-Z_mean" = "Baseline"
))

# Prep labeller
```

In this section, we present the results for the predicted probabilities part of the simulation study. Included are also the results for $CH_{1}$ (multiple imputation using only the cumulative hazard for REL) and $Ref$ (model fitted on full dataset prior to any missigness being induced). Results from the imputation methods are those with $m = 50$.

We show results at horizon of 5 years after baseline, restricting to high amount of missing (50\%). 

# 1 Continuous X

```{r mcse_contin}
mcse_bias <- preds_results[beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"][["bias_mcse"]]

mcse_rmse <- preds_results[beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"][["rmse_mcse"]]
```

- Range of Bias MCSE: [`r round(min(mcse_bias), 3)`; `r round(max(mcse_bias), 3)`]
- Range of RMSE MCSE: [`r round(min(mcse_rmse), 3)`; `r round(max(mcse_rmse), 3)`]

## 1.1 MCAR

### 1.1.1 Bias

```{r mcar_bias_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.02,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}" 
    ),
    top_step = -0.05
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.05, 0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

### 1.1.2 RMSE

```{r mcar_rmse_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.02,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}" 
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

## 1.2 MAR

### 1.2.1 Bias

```{r mar_bias_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.005,
    height_betw_steps = 0.01,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.025
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.025, 0, 0.025)) +
  ggplot2::theme(legend.position = "bottom")
```

### 1.2.2 RMSE

```{r mar_rmse_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.001,
    height_betw_steps = 0.003,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.004
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.01, 0.02)) +
  ggplot2::theme(legend.position = "bottom")
```


## 1.3 MAR-T

### 1.3.1 Bias

```{r mart_bias_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR_GEN" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.025,
    height_betw_steps = 0.05,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.2
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.1, -0.2, 0, 0.1, 0.2)) +
  ggplot2::theme(legend.position = "bottom")
```

### 1.3.2 RMSE

```{r mart_rmse_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR_GEN" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  ggplot2::theme(legend.position = "bottom")
```


## 1.4 MNAR

### 1.4.1 Bias

```{r mnar_bias_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MNAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.1
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.05, 0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

### 1.4.2 RMSE

```{r mnar_rmse_contin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MNAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("mean_X-Z_mean", "-1SD_X-Z_-1SD", "+1SD_X-Z_+1SD") & 
    X_level == "continuous"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

# 2 Binary X

```{r mcse_bin}
mcse_bias_bin <- preds_results[beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"][["bias_mcse"]]

mcse_rmse_bin <- preds_results[beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"][["rmse_mcse"]]
```

- Range of Bias MCSE: [`r round(min(mcse_bias_bin), 3)`; `r round(max(mcse_bias_bin), 3)`]
- Range of RMSE MCSE: [`r round(min(mcse_rmse_bin), 3)`; `r round(max(mcse_rmse_bin), 3)`]

## 2.1 MCAR

### 2.1.1 Bias

```{r mcar_bias_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.02,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}" 
    ),
    top_step = -0.05
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.05, 0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

### 2.1.2 RMSE

```{r mcar_rmse_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MCAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.02,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}" 
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```


## 2.2 MAR

### 2.2.1 Bias

```{r mar_bias_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.005,
    height_betw_steps = 0.01,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.025
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.025, 0, 0.025)) +
  ggplot2::theme(legend.position = "bottom")
```

### 2.2.2 RMSE

```{r mar_rmse_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.001,
    height_betw_steps = 0.003,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.004
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.01, 0.02)) +
  ggplot2::theme(legend.position = "bottom")
```


## 2.3 MAR-T

### 2.3.1 Bias

```{r mart_bias_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR_GEN" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.025,
    height_betw_steps = 0.05,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.2
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.1, -0.2, 0, 0.1, 0.2)) +
  ggplot2::theme(legend.position = "bottom")
```

### 2.3.2 RMSE

```{r mart_rmse_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MAR_GEN" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  ggplot2::theme(legend.position = "bottom")
```


## 2.4 MNAR

### 2.4.1 Bias

```{r mnar_bias_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MNAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary" & 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "bias", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.1
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Bias") +
  ggplot2::scale_y_continuous(breaks = c(-0.05, 0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

### 2.4.2 RMSE

```{r mnar_rmse_bin, fig.height=10, fig.width=11,fig.align='left'}
preds_results[
    beta1 != "0" &
    miss_mech == "MNAR" & 
    times == "5 years" &  
    `combo-X_Z` %in% c("0_X-Z_mean", "0_X-Z_-1SD", "1_X-Z_+1SD") & 
    X_level == "binary"& 
    prop_miss == "50%"
] %>% 
  ggplot_nlp(
    estim = "rmse", 
    method_var = "analy", 
    true = 0, 
    step_factors = c("state", "beta1", "haz_shape", "eta1"),
    text_size = 4, 
    pointsize = 1.5,
    point_dodge = 0.7,
    height_steps = 0.01,
    height_betw_steps = 0.03,
    step_labels = c(
      "beta1" = "Beta1 = {0.5, 1}", 
      "state" = "State = {REL, NRM}", 
      "haz_shape" = "Hazard shapes = {similar, different}", 
      "eta1" = "Mech. strength = {weak, strong}"
    ),
    top_step = -0.04
  ) +
  facet_wrap(
    . ~ `combo-X_Z`, nrow = 3, ncol = 1,
    labeller = labeller(`combo-X_Z` = patient_labs)
  ) +
  ggplot2::guides(
    shape = ggplot2::guide_legend("Method"),
    linetype = ggplot2::guide_legend("Method")
  ) +
  ggplot2::ylab("Root mean square error (RMSE)") +
  ggplot2::scale_y_continuous(breaks = c(0, 0.05)) +
  ggplot2::theme(legend.position = "bottom")
```

