---
title: "Regression coefficients: full results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Regression coefficients: full results}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  fig.retina = 3, # change to 3 
  fig.align = "center",
  fig.width = 7,
  fig.height = 4,
  #dev.args = list(bg = "transparent"),
  #fig.ext = "svg",
  echo = FALSE
)
```

```{r setup}
library(CauseSpecCovarMI)
library(ggplot2)
library(ggpubr)

theme_set(
  theme_bw(base_size = 11)
)

set.seed(1984)
```

In this section, we present the full results for the regression coefficients part of the simulation study. Included are also the results for $CH_{1}$ (multiple imputation using only the cumulative hazard for REL) and $Ref$ (model fitted on full dataset prior to any missigness being induced). Results from the imputation methods are those with $m = 50$.

```{r read}
# Read-in summarised results and scenarios
regr_results <- data.table::setDT(CauseSpecCovarMI::regr_results)
regr_results <- regr_results[n != 500]

regr_results[, var_label := factor(
  x = var,
  levels = c("X.1", "X.2", "Z.1", "Z.2"),
  labels = c(
    expression(hat(beta)[1]),
    expression(hat(beta)[2]),
    expression(hat(gamma)[1]),
    expression(hat(gamma)[2])
  )
)]

regr_results[, coverage := round(100 * cover, 0)]
regr_results[, se_round := round(se, 2)]


scenarios <- data.table::setDT(CauseSpecCovarMI::scenarios)
```

# 1 Scenarios

These were the scenarios that were run:

```{r scenarios}
scenarios[, !c("seed", "pilot")] %>% knitr::kable()
```


# 2 Continuous $X$

```{r mcse_contin}
mcse_bias <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "continuous"][["bias_mcse"]]

mcse_rmse <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "continuous"][["rmse_mcse"]]

mcse_coverage <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "continuous"][["cover_mcse"]]

mcse_se <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "continuous"][["se_mcse"]]
```

- Range of Bias MCSE: [`r round(min(mcse_bias), 3)`; `r round(max(mcse_bias), 3)`]
- Range of RMSE MCSE: [`r round(min(mcse_rmse), 3)`; `r round(max(mcse_rmse), 3)`]
- Range of Coverage MCSE: [`r round(min(mcse_coverage), 3)`; `r round(max(mcse_coverage), 3)`]
- Range of Estimated SE MCSE: [`r round(min(mcse_se), 3)`; `r round(max(mcse_se), 3)`]

## 2.1 MCAR

### 2.1.1 Bias
```{r mcar_contin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MCAR" & X_level == "continuous"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape"),#, "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.3,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}"#,
    #"eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.1, -0.2, -0.3)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```


### 2.1.2 RMSE
```{r mcar_contin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MCAR" & X_level == "continuous"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 2.1.3 Coverage

```{r mcar_contin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
# Make labellers
beta1_labs <- ggplot2::as_labeller(c("0.5" = "Beta 1 = 0.5", "1" = "Beta 1 = 1"))
eta1_labs <- ggplot2::as_labeller(c("Weak" = "Weak miss mech.", "Strong" = "Strong miss mech."))
haz_labs <- ggplot2::as_labeller(c("similar" = "Similar hazards", "different" = "Different hazards"))
propmiss_labs <- ggplot2::as_labeller(c("10%" = "Prop. miss = 10%", "50%" = "Prop. miss = 50%"))

regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MCAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 2.1.4 Estimated SE
```{r mcar_contin_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MCAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~  prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


## 2.2 MAR

### 2.2.1 Bias
```{r mar_contin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR" & X_level == "continuous"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.2,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.05, -0.1, - 0.15)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 2.2.2 RMSE

```{r mar_contin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR" & X_level == "continuous"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 2.2.3 Coverage

```{r mar_contin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 2.2.4 Estimated SE
```{r mar_contin_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


## 2.3 MAR-T

### 2.3.1 Bias
```{r mart_contin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR_GEN" & X_level == "continuous"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.325,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.1, - 0.2, -0.3)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```


### 2.3.2 RMSE

```{r mart_contin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR_GEN" & X_level == "continuous"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 2.3.3 Coverage

```{r mart_contin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR_GEN" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 2.3.4 Estimated SE
```{r mart_contin_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR_GEN" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```

## 2.4 MNAR

### 2.4.1 Bias
```{r mnar_contin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MNAR" & X_level == "continuous"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.225,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.05, -0.1, - 0.15)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```

### 2.4.2 RMSE

```{r mnar_contin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MNAR" & X_level == "continuous"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 2.4.3 Coverage

```{r mnar_contin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MNAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 2.4.4 Estimated SE
```{r mnar_contin_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MNAR" & X_level == "continuous"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


# 3. Binary $X$

```{r mcse_bin}
mcse_bias_bin <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "binary"][["bias_mcse"]]

mcse_rmse_bin <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "binary"][["rmse_mcse"]]

mcse_coverage_bin <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "binary"][["cover_mcse"]]

mcse_se_bin <- regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                            X_level == "binary"][["se_mcse"]]
```

- Range of Bias MCSE: [`r round(min(mcse_bias_bin), 3)`; `r round(max(mcse_bias_bin), 3)`]
- Range of RMSE MCSE: [`r round(min(mcse_rmse_bin), 3)`; `r round(max(mcse_rmse_bin), 3)`]
- Range of Coverage MCSE: [`r round(min(mcse_coverage_bin), 3)`; `r round(max(mcse_coverage_bin), 3)`]
- Range of Estimated SE MCSE: [`r round(min(mcse_se_bin), 3)`; `r round(max(mcse_se_bin), 3)`]


## 3.1 MCAR

### 3.1.1 Bias
```{r mcar_contin_bin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MCAR" & X_level == "binary"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape"),#, "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.3,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}"#,
    #"eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.1, -0.2, -0.3)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```

### 3.1.2 RMSE

```{r mcar_bin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MCAR" & X_level == "binary"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 3.1.3 Coverage

```{r mcar_bin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MCAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 3.1.4 Estimated SE
```{r mcar_binary_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MCAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```

## 3.2 MAR

### 3.2.1 Bias

```{r mar_contin_bin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR" & X_level == "binary"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.2,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.05, -0.1, - 0.15)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```


### 3.2.2 RMSE

```{r mar_bin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR" & X_level == "binary"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 3.2.3 Coverage

```{r mar_bin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 3.2.4 Estimated SE
```{r mar_binary_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


## 3.3 MAR-T

### 3.3.1 Bias

```{r mart_contin_bin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR_GEN" & X_level == "binary"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.325,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.1, - 0.2, -0.3)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```

### 3.3.2 RMSE

```{r mart_bin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MAR_GEN" & X_level == "binary"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 3.3.3 Coverage

```{r mart_bin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR_GEN" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 3.3.4 Estimated SE
```{r mart_binary_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MAR_GEN" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```

## 3.4 MNAR

### 3.4.1 Bias

```{r mnar_contin_bin, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MNAR" & X_level == "binary"],
  estim = "bias", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.225,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, -0.05, -0.1, - 0.15)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("Bias") +
  theme(legend.position = "bottom", 
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size=15)) 
```

### 3.4.2 RMSE

```{r mnar_bin_rmse, echo=FALSE, fig.height=14, fig.width=11,fig.align='left'}
ggplot_nlp(
  dat = regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
                       miss_mech == "MNAR" & X_level == "binary"],
  estim = "rmse", 
  method_var = "analy", 
  true = 0, 
  step_factors = c("beta1", "prop_miss", "haz_shape", "eta1"),
  point_dodge = 0.7,
  text_size = 4, 
  pointsize = 1.5, 
  height_steps = 0.03,
  height_betw_steps = 0.05,
  top_step = -0.1,
  step_labels = c(
    "beta1" = "Beta1 = {0.5, 1}",
    "prop_miss" = "Missing % = {10, 50}", 
    "haz_shape" = "Hazard shapes = {similar, different}",
    "eta1" = "Mech. strength = {weak, strong}"
  )
  ) +
  ggplot2::guides(shape = guide_legend("Method"),
                  linetype = guide_legend("Method")) +
  theme_minimal(base_size = 12) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2)) +
  facet_wrap(. ~ var_label, nrow = 4, ncol = 1, labeller = label_parsed) +
  ylab("RMSE") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    strip.text = element_text(size=15)
  ) 
```

### 3.4.3 Coverage

```{r mnar_bin_cover, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MNAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = cover, label = coverage)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient2(midpoint = 0.95, limits = c(0, 1), 
                       low = "darkblue", 
                       high = "red",
                       mid = "yellow", breaks = c(0, .5, 1)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```


### 3.4.4 Estimated SE
```{r mnar_binary_se, echo=FALSE, fig.height=11, fig.width=11,fig.align='left'}
regr_results[m %in% c(0, 50) & n == 2000 & beta1 != "0" & 
               miss_mech == "MNAR" & X_level == "binary"] %>% 
  ggplot(aes(x = analy, y = var, fill = se, label = se_round)) +
  geom_tile() +
  geom_text(col = "black") +
  scale_fill_gradient(limits = c(0, 0.2), 
                       low = "yellow", 
                       high = "darkblue", breaks = c(0, .1, .2)) +
  #ggplot2::scale_fill_brewer() +
  facet_grid(
    beta1 * haz_shape ~ eta1 * prop_miss, 
    labeller = labeller(beta1 = beta1_labs, 
                        eta1 = eta1_labs,
                        haz_shape = haz_labs, 
                        prop_miss = propmiss_labs)
  ) +
  coord_cartesian(expand = 0) +
  scale_y_discrete(labels = parse(text = levels(regr_results$var_label))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylab("Coefficient") +
  xlab("Method") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top")
```
